Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-09-07 article.tex
Update MMS plots

Figure \ref{fig:mms_accuracy}(a) shows the displacement magnitude discretisation errors ($L_2$ and $L_\infty$) as a function of the average cell width for both the hexahedral and polyhedral meshes.
Figure \ref{fig:mms_accuracy}(b) shows the corresponding order of accuracy plots.
The maximum ($L_\infty$) and average ($L_2$) discretisation errors are seen to reduce at an approximately second-order rate for both hexahedral and polyhedral meshes, where the errors are smaller on the hexahedral meshes \hl{check}.
The discretisation errors in the $\sigma_{xx}$ component of stress are shown in Figure \ref{fig:mms_accuracy}(b), and the order of accuracy in \ref{fig:mms_accuracy}(d).
The order of accuracy for the average stress magnitude error is seen to be \hl{XX} for the hexahedral meshes and just over 1.5 for the polyhedral meshes.
In contrast, the maximum stress error order of accuracy is seen to be 1 for both mesh types \hl{check}.
\begin{figure}[htbp]
	\centering
	\subfigure[Displacement magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_poly_dispErrors} 
   	}
	\subfigure[Displacement discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_poly_orderOfAccuracy}  
   	}
	\subfigure[Stress magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_poly_stressErrors} 
   	}
	\subfigure[Strress discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_poly_orderOfAccuracy}  
   	}
	\caption{Manufactured solution cube case: the accuracy and order of accuracy for displacement and stress \hl{update plots}: 4 plots - disp error (hex, poly), stress error (hex, poly), disp order (hex, poly), stress order (hex, poly). Use same xrange for all. Put name of 1st/2nd order slope on the line rather than in the legend }
	\label{fig:mms_accuracy}
\end{figure}

>>>>

Figure \ref{fig:mms_accuracy}(a) shows the displacement magnitude discretisation errors ($L_2$ and $L_\infty$) as a function of the average cell width for both the hexahedral and polyhedral meshes.
Figure \ref{fig:mms_accuracy}(b) shows the corresponding order of accuracy plots.
The maximum ($L_\infty$) and average ($L_2$) discretisation errors are seen to reduce at an approximately second-order rate for both hexahedral and polyhedral meshes, where the errors are smaller on the hexahedral meshes \hl{check}.
The discretisation errors in the $\sigma_{xx}$ component of stress are shown in Figure \ref{fig:mms_accuracy}(b), and the order of accuracy in \ref{fig:mms_accuracy}(d).
The order of accuracy for the average stress magnitude error is seen to be \hl{XX} for the hexahedral meshes and just over 1.5 for the polyhedral meshes.
In contrast, the maximum stress error order of accuracy is seen to be 1 for both mesh types \hl{check}.
\begin{figure}[htbp]
	\centering
	\subfigure[Displacement magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_dispErrors} 
   	}
	\subfigure[Displacement discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_disp_orderOfAccuracy}  
   	}
	\subfigure[Stress magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_stressErrors} 
   	}
	\subfigure[Stress discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_stress_orderOfAccuracy}  
   	}
	\caption{Manufactured solution cube case: the accuracy and order of accuracy for displacement and stress}
	\label{fig:mms_accuracy}
\end{figure}
